Tree height, microhabitat, and hydraulic traits shape drought responses in a temperate broadleaf forest

### 2019-09-21 manuscript/climate_sensitivity_draft.Rmd
worked on discussion

@@

6. we advance knowledge regarding differences across droughts ??
  - biophysical mechanisms are things that should be seen as universal but relative importance of each can vary within each drought (or across sites)

>>>>

Although the physiological mechanisms discussed above lead to generally consistent directions of growth responses to tree height and hydaulic traits across droughts, indicating the universality of the underlying mechanisms, the relative importantance of the drivers varied widely across droughts, indicating an interaction with drought characteristics (Tables 4-5). [**DISCUSS DIFFERENCES ACROSS DROUGHTS-- e.g., 1966 was preceded by two dry years, and height mattered most in this drought. ...**] Further research will be required to understand how drought characteristics interact with driver variables to shape tree growth responses.

Our study reveals that tree height, microhabitat, and species' hydraulic traits interactively shape tree growth responses to drought.

@@

6. we advance knowledge regarding differences across droughts
